%-------------------------
% Resume in Latex
% Author : Jake
% Modified for: Rahul Nayanegali
% License : MIT
%-------------------------

\documentclass[letterpaper,11pt]{article}
\usepackage{lmodern}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1


%-------------------------
% Custom Commands
\newcommand{\resumeItem}[1]{
  \item\small{{#1 \vspace{-2pt}}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%% RESUME STARTS HERE %%%%%%%%%%%%%%%%%%
\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Rahul Anand Nayanegali} \\ \vspace{1pt}
    \small 551-399-9002 $|$ \href{mailto:nayanegali.rahul@gmail.com}{\underline{nayanegali.rahul@gmail.com}} $|$
    \href{https://linkedin.com/in/rahulnayanegali}{\underline{Linkedin}} $|$
    \href{https://rahulnayanegali.dev}{\underline{rahulnayanegali.dev}} $|$ New York Metropolitan Area
\end{center}

%-----------SUMMARY-----------
\section{Summary}
  \small{
    Software Engineer with extensive experience building scalable web applications using \textbf{React}, \textbf{TypeScript}, and \textbf{Micro Frontends}. Deep expertise in component architecture, state management, and modern frontend development practices. Proficient in \textbf{Python (Flask) and Node.js} for backend services, real-time data streaming, and data processing. Skilled in \textbf{robust API integration} and \textbf{error handling strategies}, driving technical excellence through \textbf{TDD} and \textbf{Clean Architecture}. Strong communicator who thrives on \textbf{pair programming}, knowledge sharing, and translating ambiguous business requirements into high-quality technical solutions.
  }

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
\textbf{Frontend}{: React, TypeScript, Next.js, Web Components, JavaScript, State Management (Redux, Apollo Client)} \\
      \textbf{Architecture}{: Micro Frontends (Module Federation), Monorepos (NX), Functional Programming, TDD, Clean Architecture, SOLID} \\
      \textbf{AI-Augmented Engineering}{: AI-powered development workflows using Kiro, Claude Code, OpenCode CLI, MCP; Prompt engineering (CoT, Few-Shot) to accelerate delivery; context optimization for efficient AI collaboration.} \\ 
     \textbf{Testing}{: React Testing Library, Jest, Playwright, Cypress} \\
     \textbf{Backend}{: Python, Flask, Node.js, REST APIs, GraphQL, WebSockets, SSE (Real-Time)} \\
     \textbf{Cloud \& Tools}{: AWS (ECS, EC2, S3, Lambda, CloudFront), Docker, Chrome Extensions, Vite/Webpack, NX, Git, CI/CD pipelines} \\
     \textbf{Soft Skills}{: Proactive Communication, Pair Programming, Code Reviews, Whiteboarding} \\
    }}
 \end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    % Amazon
    \resumeSubheading
      {Software Development Engineer (Frontend)}{Jun 2025 -- Dec 2025}
      {Amazon (Contract via Lares IT Solutions Inc)}{Seattle, WA}
      \resumeItemListStart
        \resumeItem{Decoupled a business-critical \textbf{React + TypeScript} frontend using the \textbf{Strangler Fig} pattern, incrementally migrating legacy flows to \textbf{micro-frontends (Module Federation)} with zero production downtime.}
        \resumeItem{Built and evolved schema-driven UI modules in \textbf{React}, contributing core capabilities to \textbf{ActionWidget}, a micro-frontend workflow engine that renders dynamic, compliance-heavy user flows.}
        \resumeItem{Integrated complex backend APIs into the frontend through well-defined contracts, implementing robust \textbf{error handling}, validation, and edge-case management for high-reliability user journeys.}
        \resumeItem{Designed AI-assisted testing workflows by authoring BDD-style specifications, enabling LLM-assisted autonomous generation of \textbf{Playwright} integration tests and expanding test coverage.}
        \resumeItem{Raised code review quality by enforcing single-purpose diffs, separating structural refactors from behavioral changes to reduce cognitive load, isolate risk, and enable safer incremental evolution of the codebase.}
        \resumeItem{Accelerated delivery and code quality through \textbf{pair programming}, design reviews, and shared frontend standards across a distributed engineering team.}
      \resumeItemListEnd
        
        % Shoptaki
        \resumeSubheading
        {Software Engineer}{Aug 2024 -- Jun 2025}
        {Shoptaki}{New York, NY}
        \resumeItemListStart
        \resumeItem{Implemented reusable components with TypeScript \& Storybook, reducing development time by 20\% \& maintaining UI consistency across web \& mobile apps, enhancing scalability.}
        \resumeItem{Developed \textbf{Python} data processing pipelines and reporting services, leveraging PostgreSQL for structured storage and enabling analytics across the platform.}
        \resumeItem{Designed and optimized RESTful APIs using Node.js and ArangoDB, improving data retrieval and reducing backend processing time by 25\%.}
      \resumeItemListEnd

    % CodeCraft
    \resumeSubheading
      {Engineer, Web Development}{Feb 2021 -- Jan 2023}
      {CodeCraft Technologies}{Bangalore, India}
      \resumeItemListStart
        \resumeItem{Established a Test-Driven Development (TDD) environment for an IoT project by integrating React Storybook and Jest, which reduced post-deployment bugs by 40\% and was adopted as the standard boilerplate for company projects.}
        \resumeItem{Built and maintained backend services in \textbf{Node.js} and Python, deployed on Amazon ECS and EC2; utilized S3 for file storage and AWS Lambda for background data processing.}
        \resumeItem{Migrated application state from Redux to Apollo Client (GraphQL), optimizing data fetching patterns and implementing a unified GraphQL infrastructure layer; eliminated boilerplate code and reduced bundle size by 20\%.}
        \resumeItem{Integrated Storybook to decouple UI development from backend dependencies, enabling parallel development streams and ensuring rigorous component isolation for the UI library.}
        \resumeItem{Modernized the build infrastructure for a high-traffic streaming platform, optimizing asset delivery and upgrading Webpack/Babel to slash build times by 50\% and enable ES6+ features.}
      \resumeItemListEnd

    % TCS
    \resumeSubheading
      {Assistant Systems Engineer}{Nov 2018 -- Apr 2020}
      {Tata Consultancy Services}{Bangalore, India}
      \resumeItemListStart
        \resumeItem{Built \textbf{real-time IoT dashboard} using React, Flask, and Server-Sent Events (SSE) for live sensor monitoring, handling continuous data streams at scale.}
        \resumeItem{Built backend services in \textbf{Python (Flask)}, exposing RESTful API endpoints for authentication, data retrieval, and real-time updates; integrated with React frontend for seamless data flow.}
        \resumeItem{Collaborated with UI/UX designers to translate wireframes and prototypes into functional, visually appealing web interfaces, ensuring accessibility and consistency.}
        \resumeItem{Optimized front-end performance using techniques such as lazy loading, image compression, JavaScript minification, and elimination of render-blocking resources for faster load times.}
        \resumeItem{Managed source code efficiently using Git and GitHub, implementing version control best practices, code reviews, and structured branching strategies.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Pace University}{New York, NY}
      {Master of Science in Computer Science}{}
      \resumeItemListStart
        \resumeItem{Received the Computer Science Departmental Award for outstanding academic performance.}
      \resumeItemListEnd
      \resumeSubheading
        {Sri Siddhartha Institute of Technology}{Tumkur, India}
        {Bachelor of Engineering in Electronics and Communication Engineering}{}
        \resumeItemListStart
         \resumeItem{Received the Outstanding IEEE Student Volunteer Award}
        \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------CERTIFICATIONS-----------
\section{Certifications}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{AWS Certified Cloud Practitioner} \\
     \textbf{Master JavaScript} -- LinkedIn Learning \\
    }}
 \end{itemize}

\end{document}
