%-------------------------
% Resume in Latex
% Author : Jake
% Modified for: Rahul Nayanegali
% License : MIT
%-------------------------

\documentclass[letterpaper,11pt]{article}
\usepackage{lmodern}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1


%-------------------------
% Custom Commands
\newcommand{\resumeItem}[1]{
  \item\small{{#1 \vspace{-2pt}}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%% RESUME STARTS HERE %%%%%%%%%%%%%%%%%%
\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Rahul Nayanegali} \\ \vspace{1pt}
    \small 551-399-9002 $|$ \href{mailto:nayanegali.rahul@gmail.com}{\underline{nayanegali.rahul@gmail.com}} $|$
    \href{https://linkedin.com/in/rahulnayanegali}{\underline{Linkedin}} $|$
    \href{https://rahulnayanegali.dev}{\underline{rahulnayanegali.dev}} $|$ New York Metropolitan Area
\end{center}

%-----------SUMMARY-----------
\section{Summary}
  \small{
    Software Engineer with deep expertise in building scalable web applications using \textbf{React}, \textbf{TypeScript}, \textbf{Node.js}, and \textbf{Micro Frontends}. Skilled in \textbf{robust API integration} and \textbf{error handling strategies}, driving technical excellence through \textbf{TDD} and \textbf{Clean Architecture}. Strong communicator who thrives on \textbf{pair programming}, knowledge sharing, and translating ambiguous business requirements into high-quality technical solutions.
  }

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Frontend}{: React, TypeScript, Next.js, Web Components, JavaScript} \\
     \textbf{Architecture}{: Micro Frontends (Module Federation), Monorepos (NX/Turborepo), Functional Programming, TDD, Clean Architecture, SOLID} \\
     \textbf{Testing}{: React Testing Library, Jest, Playwright, Cypress} \\
     \textbf{Backend}{: Node.js, GraphQL (Apollo Client), REST APIs, Java} \\
     \textbf{Cloud}{: AWS (ECS, EC2, S3, Lambda, CloudFront)} \\
     \textbf{Tools}{: Chrome Extensions, Vite/Webpack, NX, CircleCI, Git, CI/CD pipelines} \\
     \textbf{Soft Skills}{: Proactive Communication, Pair Programming, Code Reviews, Whiteboarding} \\
    }}
 \end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    % Amazon
    \resumeSubheading
      {Software Development Engineer (Frontend)}{Jun 2025 -- Dec 2025}
      {Amazon (Contract via Lares IT Solutions Inc)}{Seattle, WA}
      \resumeItemListStart
        \resumeItem{Decoupled a business-critical platform using the Strangler Fig pattern, enabling incremental migration to a modular declarative architecture with zero production downtime.}
        \resumeItem{Leveraged AI-powered coding tools to automate boilerplate generation, reducing cognitive overhead and accelerating the delivery of complex architectural features.}
        \resumeItem{Contributed key modules for ActionWidget, a micro-frontend engine that orchestrates complex compliance workflows through dynamic, schema-driven UI rendering.}
        \resumeItem{Collaborated with stakeholders to decompose ambiguous business rules into discrete workflow schemas, enabling the incremental delivery of shippable features.}
        \resumeItem{Accelerated the development of integration suites by defining BDD specifications that provide context for LLMs, enabling the autonomous generation of Playwright tests.}
        \resumeItem{Cultivated a collaborative culture of pair programming and code reviews, accelerating team velocity without compromising on code quality.}
      \resumeItemListEnd
        
        % Shoptaki
        \resumeSubheading
        {Software Engineer}{Aug 2024 -- Jun 2025}
        {Shoptaki}{New York, NY}
        \resumeItemListStart
        \resumeItem{Implemented reusable components with TypeScript \& Storybook, reducing development time by 20\% \& maintaining UI consistency across web \& mobile apps, enhancing scalability.}
        \resumeItem{Designed and optimized RESTful APIs using Node.js with ArangoDB, improving graph data retrieval and reducing backend processing time by 25\%.}
        \resumeItem{Designed a service-oriented architecture and defined strict API interfaces with clear separation of concerns between UI, content scripts, and background processes.}
      \resumeItemListEnd

    % CodeCraft
    \resumeSubheading
      {Engineer, Web Development}{Feb 2021 -- Jan 2023}
      {CodeCraft Technologies}{Bangalore, India}
      \resumeItemListStart
        \resumeItem{Established a Test-Driven Development (TDD) environment for an IoT project by integrating React Storybook and Jest, which reduced post-deployment bugs by 40\% and was adopted as the standard boilerplate for company projects.}
        \resumeItem{Built and maintained backend services deployed on Amazon ECS and EC2, utilizing S3 for reliable file storage and writing AWS Lambda functions to handle background data processing for the IoT project.}
        \resumeItem{Migrated application state from Redux to Apollo Client (GraphQL), optimizing data fetching patterns and implementing a unified GraphQL infrastructure layer; eliminated boilerplate code and reduced bundle size by 20\%.}
        \resumeItem{Integrated Storybook to decouple UI development from backend dependencies, enabling parallel development streams and ensuring rigorous component isolation for the UI library.}
        \resumeItem{Modernized the build infrastructure for a high-traffic streaming platform, optimizing asset delivery and upgrading Webpack/Babel to slash build times by 50\% and enable ES6+ features.}
      \resumeItemListEnd

    % TCS
    \resumeSubheading
      {Assistant Systems Engineer}{Nov 2018 -- Apr 2020}
      {Tata Consultancy Services}{Bangalore, India}
      \resumeItemListStart
        \resumeItem{Built real-time IoT dashboard using React, Flask, SSE, and AWS Lambda for large-scale sensor monitoring.}
        \resumeItem{Integrated front-end applications with Flask APIs and RESTful services, handling authentication, data retrieval, and real-time updates to ensure seamless data flow.}
        \resumeItem{Collaborated with UI/UX designers to translate wireframes and prototypes into functional, visually appealing web interfaces, ensuring accessibility and consistency.}
        \resumeItem{Optimized front-end performance using techniques such as lazy loading, image compression, JavaScript minification, and elimination of render-blocking resources for faster load times.}
        \resumeItem{Managed source code efficiently using Git and GitHub, implementing version control best practices, code reviews, and structured branching strategies.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Pace University}{New York, NY}
      {Master of Science in Computer Science}{}
      \resumeItemListStart
        \resumeItem{Received the Computer Science Departmental Award for outstanding academic performance.}
      \resumeItemListEnd
      \resumeSubheading
        {Sri Siddhartha Institute of Technology}{Tumkur, India}
        {Bachelor of Engineering in Electronics and Communication Engineering}{}
        \resumeItemListStart
         \resumeItem{Received the Outstanding IEEE Student Volunteer Award}
        \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------CERTIFICATIONS-----------
\section{Certifications}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{AWS Certified Cloud Practitioner} \\
     \textbf{Master JavaScript} -- LinkedIn Learning \\
    }}
 \end{itemize}

\end{document}
